\textbf{Specification: Providing an Access Control Layer in Content Distribution Networks}

### 2015-09-21 tex/spec.tex
Added some introduction

\title{\textbf{Specification: Providing Access Control in Content Distribution Networks}}
\author{Lukas Klingsbo}

@@

\clearpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Background}
This work will be done at the company Uprise (Dragarbrunnsgatan 36C, Uppsala). 
The goal of this project is to explore, and creating, the possibility to have 
access control in a content distribution network.

@@

\section{Methods}
\begin{itemize}
  \item The prototype/system will be developed in Scala. 
  \item A literature study will be done once the specification is accepted. 
  \item Results will be evaluated from a security and scalability point of view. 
  \item A work station and desk space will be provided by Uprise.
\end{itemize}

@@

\section{References}
One possibility to develop a solution from:

>>>>

\title{\textbf{Specification: Providing an Access Control Layer in Content Distribution Networks}}
\author{Lukas Klingsbo}

@@

\clearpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Background}
This work will be done at the company Uprise (Dragarbrunnsgatan 36C, Uppsala). 
The goal of this project is to explore, and creating, the possibility to have 
an local access control layer for files in a content distribution network.
This will make it easier to have control over the security settings of the 
projects and will also make it possible to enforce local (as in not on the CDN) 
auth and audit logging.

@@

It should also be possible to create so called views and projects which a group 
of files are added to, which then have their own security settings.

\section{Methods}
\begin{itemize}
  \item The prototype/system will be developed in Scala and React. 
  \item A literature study will be done once the specification is accepted. 
  \item Results will be evaluated from a security and scalability point of view. 
  \item A work station and desk space will be provided by Uprise.
\end{itemize}

@@

\section{References}
One possibility to connect the backend to:
